---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slideimp.extra

<!-- badges: start -->
<!-- badges: end -->

`{slideimp.extra}` contains helpful tools for [`{slideimp}`](https://github.com/hhp94/slideimp) such as the downloading of Illumina manifests for the `slideimp::prep_groups()` function.

## Installation

You can install the development version of `{slideimp.extra}` with `{pak}` or `remotes::install_github()`:

``` r
pak::pak("hhp94/slideimp.extra")
```

## Path Management
```{r, include = FALSE}
library(slideimp.extra)
set.seed(1234)
```

The `slideimp` package manages its data directory path via the environment variable `SLIDEIMP`, with options for session-based or consistent overrides.

```{r, eval = F}
# **Get default path**:
get_slideimp_path()
# **Create and verify writable path**:
get_slideimp_path(create = TRUE)
# **Set temporary path for session**:
set_slideimp_path("/your/custom/path")
# **Reset to default**:
set_slideimp_path(NULL)
```

- **Consistent override**: 
Add to `~/.Renviron` (i.e., `file.edit("~/.Renviron")`) and reset your R session:
```{bash, eval = F}
SLIDEIMP=/your/custom/path
```

## Download Manifests
Use `ilmn_manifest()` to download the included manifests. Run without an argument to print available options:

```{r}
ilmn_manifest()
```

The first time the function is called for a manifest, it attempts to download, clean, and store it under the path at `get_slideimp_path()`.

```{r, eval = F}
# Download and clean the MSA manifest and store the object at `get_slideimp_path()`
ilmn_manifest("MSA")
# Download 'MSA' manifest? [y/n]: y
```

The path to the cleaned manifest can be fetched with `get_manifest()`.

```{r, eval = F}
get_manifest("MSA")
```

We can now read the manifest into memory and use it with the `slideimp::prep_groups()` function from `{slideimp}` to perform grouped imputation with `slideimp::group_imp()`.

```{r, include=FALSE, echo=FALSE}
set_slideimp_path("dev")
get_manifest("MSA", rawdir = "dev")
```

```{r}
set.seed(1234)
msa <- ilmn_manifest("MSA")
head(msa)
```

Clear the downloaded files with `clear_cache()`
```{r, eval = F}
clear_cache()
# The following files will be deleted:
#   - 'dev/MSA/MSA.fst'
# confirm deletion? [y/n]: y
```

